### 2020-10-01 written/software/software_design.tex
added recent notes

\subsection{EPI class diagram}
\begin{tikzpicture} 
\begin{umlpackage}{epi}
\umlclass{Model}{ 
  \# \_name : string \\ 
  \# \_parameters : list of parameters \\ 
  }
  { 
  + set\_name() \\
  + set\_parameters() \\
  + set\_eps() \\
  + eps() \\
  + epi() \\
  + load\_epi\_dist() \\
}

\umlclass[x=7, y=0]{Parameter}{ 
  \# \_name : string \\ 
  \# \_range : [float, float] \\ 
  }
  { 
  + set\_name() \\
  + set\_range() \\
}

\umlclass[x=0, y=-6]{Architecture}{ 
  \# \_type : string \\ 
  \# \_num\_layers : pos int \\ 
  \# \_post\_affine : bool \\
  }
  { 
  + set\_type() \\
  + set\_num\_layers() \\
  + set\_post\_affine() \\
  + to\_string() \\
  + to\_model() \\
}

\umlclass[x=-1, y=-12]{CouplingArch}{ 
  \# \_type : string \\ 
  \# \_repeats : pos int \\ 
  \# \_num\_couplings : pos int \\ 
  \# \_layers\_per\_coupling : pos int \\ 
  \# \_units\_per\_layer : pos int \\ 
  }
  { 
  + set\_repeats() \\
  + set\_num\_couplings() \\
  + set\_layers\_per\_coupling() \\
  + set\_units\_per\_layer() \\
  + to\_string() \\
  + to\_model() \\
}

\umlclass[x=6, y=-12]{AutoregressiveArch}{ 
  \# \_type : string \\ 
  \# \_repeats : pos int \\ 
  \# \_layers\_per\_conditional : pos int \\ 
  \# \_units\_per\_layer : pos int \\ 
  }
  { 
  + set\_repeats() \\
  + set\_layers\_per\_conditional() \\
  + set\_units\_per\_layer() \\
  + to\_string() \\
  + to\_model() \\
}

>>>>

\subsection{EPI class diagram}
\begin{tikzpicture} 
\begin{umlpackage}{epi}
\umlclass{Model}{ 
  + name : string \\ 
  + parameters : list of parameters \\ 
  }
  { 
  \# \_set\_name() \\
  \# \_set\_parameters() \\
  + set\_eps() \\
  + eps() \\
  + epi() \\
  + load\_epi\_dist() \\
}

\umlclass[x=7, y=0]{Parameter}{ 
  + name : string \\ 
  + bounds : [float, float] \\ 
  }
  { 
  \# \_set\_name() \\
  \# \_set\_bounds() \\
}

\umlclass[x=0, y=-6]{Architecture}{ 
  + arch\_type : string \\ 
  + num\_layers : pos int \\ 
  + post\_affine : bool \\
  }
  { 
  + \_\_call\_\_() \\
  + \_set\_type() \\
  + \_set\_num\_layers() \\
  + \_set\_post\_affine() \\
  + to\_string() \\
  + to\_model() \\
}

\umlclass[x=-1, y=-12]{CouplingArch}{ 
  + D : pos int \\ 
  + num\_couplings : pos int \\
  + num\_units : pos int \\  
  }
  { 
  + \_\_call\_\_() \\
  \# \_set\_D() \\
  \# \_set\_num\_couplings() \\
  \# \_set\_num\_units() \\
  + to\_string() \\
}

\umlclass[x=6, y=-12]{AutoregressiveArch}{ 
  + D : pos int \\ 
  + num\_couplings : pos int \\
  + num\_units : pos int \\  
  }
  { 
  + \_\_call\_\_() \\
  \# \_set\_D() \\
  \# \_set\_num\_ars() \\
  \# \_set\_num\_units() \\
  + to\_string() \\
}
